Facilities, Equipment, and Other Resources at Indiana University

### 2016-11-25 proposal/amr-bio.tex
amr-bio.tex Finish putting everything into bibLaTeX...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\nocite{DQT2014, geometry2013, VDS2009, AGVS2005, VAS2006}
\printbibliography[title={Closely Related Publications}]

\section*{Other Significant Publications}

\begin{enumerate}

\item Jacques Carette and Amr Sabry, ``Computing with Semirings and Weak Rig
  Groupoids.'' In the \emph{European Symposium on Programming}, ESOP 2016.

\item Roshan P. James and Amr Sabry, ``Information Effects.'' In the
  \emph{Conference Record of the ACM Symposium on Principles of Programming
  Languages}, 2012.

\item Amr Sabry, ``Side Effects.'' In \emph{Wiley Encyclopedia of Computer
  Science and Engineering, 5-Volume Set}, Volume 4, pages 2534-2543, Benjamin
  W. Wah (Editor), Hoboken: John Wiley \& Sons, Inc, January 2009.

\item Eugenio Moggi and Amr Sabry: Monadic encapsulation of effects: 
a revised approach (extended version). \emph{J. Funct. Program.} 11(6):
591-627 (2001)

\item Cormac Flanagan, Amr Sabry, Bruce F. Duba, and Matthias Felleisen:
The Essence of Compiling with Continuations. In the Proceedings of the ACM
SIGPLAN Conference on Programming Language Design and Implementation, pages
237-247, 1993. \emph{Selected as one of the best 50 PLDI papers from
1979-1999.}
\end{enumerate}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{refsection}
\nocite{DQT2014, geometry2013, VDS2009, AGVS2005, VAS2006}
\printbibliography[title={Closely Related Publications}]
\end{refsection}

\begin{refsection}
\nocite{CaretteSabry2016, JamesSabry2012, Sabry2009, MoggiSabry2001, FSDF1993}
\printbibliography[title={Other Significant Publications}]
\end{refsection}
